---
title: "My Fancy Presentation"
author: "Juan Sebastián Beleño Díaz"
date: "7/10/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide
Some content


***
A slide without a title

## My title
### A top level subheading
#### A second level subheading

## Slide with Items

1. Item 1
2. Item 2
3. Item 3

## Slide with Text Styles

Plain text

*Italicized text*

**Bold Text**

`for (i %in% 1 : 10)`

```{r, comment="", echo=TRUE, eval=TRUE}
head(mtcars)
```

## Plots
```{r, echo=FALSE, fig.align='center', fig.cap='My AWESOME figure'}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

